Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-11-22 patchy-selection-paper.tex
new fig

>>>>

%%%%%%%%%
\subsection{Comparison to simulation}
\label{ss:comparison_to_sims}

We used the simulations describe above to test the theory,
etcetera.

\begin{figure}[ht!]
  \begin{center}
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(A)} Time to adaptation by new mutation 
      in 3,128 simulations,
      compared to the value predicted by equation X.
      For each of 52 different parameter combinations (Supp Table XX),
      we performed between 40 and 100 independent simulations;
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination (example runs in Supp Figure XX).
      \textbf{(A)} Similar, for time to adaptation by migration
      in 4,158 simulations.
      TODO: put equations on axis labels, describe more, make supp figs.
  }   \label{fig:sim_times}
\end{figure}
